### 2023-03-14 resilience.tex
up

In a reset petri-net, if $Bad = \uparrow q_0(\mu)$ for some $\mu \neq 0$,
and $Safe = \downarrow q(0)$,
then the resilience problem is basically \textcolor{red}{(is it?)} the single-state zero-reachability problem, and is undecidable.

>>>>

In a reset petri-net, if $Bad = \uparrow \mu$ for some $\mu \neq 0$,
and $Safe = \downarrow 0$,
then the resilience problem is basically \textcolor{red}{(is it?)} the single-state zero-reachability problem, and is undecidable.
